---
title: "Dashboard Visualization"
date: "Last Update: `r format(Sys.time(), '%Y-%m-%d')`"
output: 
  flexdashboard::flex_dashboard
---

```{r render, eval = FALSE}
# Render Command
rmarkdown::render("dashboard-part.Rmd", output_format = "flexdashboard::flex_dashboard", output_dir = "../docs/")
```

# Visualization
```{r include=FALSE}
# Library & Dataset Import
library(tidyverse)
library(plotly)
library(flexdashboard)

library(p8105.datasets)
```

```{r}
data("ny_noaa")
```

Column {data-width=600}
-----------------------------------------------------------------------

### Record count of each station

```{r}
ny_noaa |>
  drop_na() |>
  count(id) |>
  mutate(id = fct_reorder(id, n)) |>
  plot_ly(x = ~id, y = ~n, color = ~id, type = "bar", colors = "viridis") 
```

Column {data-width=400}
-----------------------------------------------------------------------

### Precipitation amount barplot for stations with top 5 record count

```{r}
ny_noaa |>
  drop_na() |> 
  filter(
    id %in% c("USW00094789", "USW00014732", "USW00014771", "USW00014768", "USW00004725"), 
    prcp > 0
  ) |>
  mutate(id = fct_reorder(id, prcp)) |>
  plot_ly(y = ~prcp, color = ~id, type = "box", colors = "viridis")
```

### Monthly mean precipitation amount for stations with top 3 record count in 21st century

```{r}
line_plot = ny_noaa |>
  drop_na() |> 
  filter(
    id %in% c("USW00094789", "USW00014732", "USW00014771"),
    year(date) >= 2000) |>
  mutate(year = year(date), month = month(date)) |>
  group_by(year, month, id) |>
  summarise(mean_prcp_monthly = mean(prcp)) |> 
  mutate(time_tick = ym(paste(year, month, sep = '-'))) |>
  ggplot(aes(x = time_tick, y = mean_prcp_monthly, color = id)) + 
  geom_line(alpha = .6) + 
  theme_bw() +
  labs(x = "Time", y = "Monthly Precipitation")

ggplotly(line_plot)
```
# Supplemental Information
**Data**: The National Oceanic and Atmospheric Association (NOAA) of the National Centers for Environmental Information (NCEI) provides public access to some weather data, including the GHCN (Global Historical Climatology Network)-Daily database of summary statistics from weather stations around the world.

**Variables**:

- `id`: Weather station ID

- `date`: Date of observation

- `prcp`: Precipitation (tenths of mm)

- `snow`: Snowfall (mm)

- `snwd`: Snow depth (mm)

- `tmax`: Maximum temperature (tenths of degrees C)

- `tmin`: Minimum temperature (tenths of degrees C)


# Other Pages
- [Home Page](index.html): home page
- [Resume Page](resume.html): Resume webpage

- [Dashboard Page](dashboard-part.html): flexdashboard for visualization